---
title: "rvest with patent lens"
author: "Paul Oldham"
date: "29 June 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Lens Locations

page 0 is page 1
page 1 is page 2
page 2 is page 3

structure of url. The first page. 50 can be specified.

```{r cars}
https://www.lens.org/lens/search?q=%22synthetic+biology%22&p=0&n=50
```


div div .result

.resultCount
.breadnum is the number of families

Full text search

```{r}
"https://www.lens.org/lens/search?q=%22synthetic+biology%22&l=en" #full text

"https://www.lens.org/lens/search?q=%28title%3A%28%22synthetic+biology%22%29+%7C%7C+abstract%3A%28%22synthetic+biology%22%29+%7C%7C+claims%3A%28%22synthetic+biology%22%29%29&l=en" # TAC

"https://www.lens.org/lens/search?q=claims%3A%28%22synthetic+biology%22%29&l=en" # claims

https://www.lens.org/lens/search?q=%22synthetic+biology%22&f=true&l=en # one per family, language is english

#for any language use 
https://www.lens.org/lens/search?q=%22synthetic+biology%22&f=true

#rank by family is

https://www.lens.org/lens/search?n=50&q=%22dna%22&p=0&f=true&v=table&s=simple_family_size&d=-
https://www.lens.org/lens/search?n=10&q=%22synthetic+biology%22&f=true&p=0&s=simple_family_size&d=-
  
#rank by citations is
https://www.lens.org/lens/search?n=50&q=%22dna%22&p=0&f=true&v=table&s=citing_pub_key_count&d=-
  
https://www.lens.org/lens/search?n=10&q=%22synthetic+biology%22&f=true&p=0&s=citing_pub_key_count&d=-

  

```


The data I want is:

```{r}
library(rvest)
html <- read_html("https://www.lens.org/lens/search?q=%22synthetic+biology%22&f=true")
patno <- html_nodes(html, "#results span")
```

Use the gadget selector to work out the positions of the elements that I want. Note that the paging in the URL is important for retrieving multiple results and some code is needed for that (to calculate the total number of pages - based on 50 pages per set). However, it seems that we cannot scroll through all pages so that may be a problem. Looks like it is limited to only 500 (10 pages), per query on 50 per page. So that will be a significant issue. Will need to use a date range to limit to 500 per set (or go online and download from there which defeats the purpose)

###Selector gadget

results top bar = .resultCount
results = .resultCount
families = .breadnum

Results table

the results table is .patNo
.crumbs , .crumbs a

```{r}
library(rvest)
html <- rvest::read_html("https://www.lens.org/lens/search?q=%22synthetic+biology%22")

html <- xml2::read_html("https://www.lens.org/lens/search?q=%28title%3A%28%22synthetic+biology%22%29+%7C%7C+abstract%3A%28%22synthetic+biology%22%29+%7C%7C+claims%3A%28%22synthetic+biology%22%29%29&f=false")

#use in 
results_families <- rvest::html_nodes(html, ".crumbs") %>% 
  rvest::html_text() %>%
  stringr::str_extract_all("[[:digit:]]+")
  results <- 
  print()
  
query_reveal <- rvest::html_nodes(html, "#previousSearchText") %>%
  rvest::html_text() %>% 
  #stringr::str_replace_all(query_reveal[[1]], "\", "")
  print()



results <- rvest::html_nodes(html, ".resultCount") %>% 
  rvest::html_text() %>%
  as.numeric() %>% 
  print() # OK use me
# if families is set to true this will not work because it is presented only as results above (so a new control is needed, can be done later)

families <- rvest::html_nodes(html, ".breadnum:nth-child(4)") %>%
  rvest::html_text() %>%
  as.numeric() %>% 
  print() # Ok use me. Something has gone wrong here. Needs to be done another way.



publication_numbers <- html_nodes(html, ".link span:nth-child(2)") %>% 
  html_text() %>%
  str_replace_all(" ", "") %>%
  str_replace_all("/", "") %>% 
  print()
# returns patent numbers but with line breaks /n

lens_id <- rvest::html_nodes(html, ".lens-id a") %>% 
  rvest::html_text() %>% 
  print() # Ok use me

titles <- rvest::html_nodes(html, ".title a") %>% 
  rvest::html_text() %>% 
  print() # Ok use me

doc_type <- rvest::html_nodes(html, ".doc-type .sup-result") %>%
  rvest::html_text() %>%
  stringr::str_replace_all("       \n     \t\t", "") %>%
  stringr::str_replace_all("\n    \t", "") %>% 
  print() # Ok use me

publication_date <- rvest::html_nodes(html, ".sup-item:nth-child(1) .sup-result") %>%
  rvest::html_text() %>% 
  stringr::str_trim(side = "both") %>% 
  print() # Ok, note the use of months as character. Separate to obtain the publication year. Also could usefully convert the date to 

family_count <- rvest::html_nodes(html, ".sup-item:nth-child(2) .sup-result") %>%
  rvest::html_text() %>% 
  as.numeric() %>% 
  print()

citing_count <- rvest::html_nodes(html, ".sup-item:nth-child(3) a") %>%
  rvest::html_text() %>% 
  as.numeric() %>% 
  print()

test <- data.frame(results, families, publication_numbers, lens_id, titles, doc_type, publication_date, family_count, citing_count) %>% print()

# full_text <-  html_nodes(html, ".fa-file-text-o") %>%
#  html_text() %>% 
#  print()







crumbs <- html_nodes(html, ".crumbs") %>% 
  html_text() #returns home, families and query name. 

numbers <- html_nodes(html, "#results a span") %>% 
  html_text() # returns patent numbers but with line breaks /n




patNo <- html_nodes(html, "#results td .patNo") %>% 
  html_name()

applicants <- html_nodes(html, "#results .owner .sup-result") %>% 
  html_text() #Use this

lego_movie %>%
  html_nodes("#titleCast .itemprop") %>%
  html_text()


```



```{r}
library(rvest)
lego_movie <- read_html("http://www.imdb.com/title/tt1490017/")
lego_movie %>% 
  html_node("strong span") %>%
  html_text() %>%
  as.numeric()
```

```{r}
library(urltools)
parsed_address <- url_parse("https://www.lens.org/lens/search?q=%22synthetic+biology%22&p=0&n=50")

url_compose(parsed_address) %>% print()


url_parse("https://www.lens.org/lens/search?p=1&q=%28title%3A%28%22synthetic+biology%22%29+%7C%7C+abstract%3A%28%22synthetic+biology%22%29+%7C%7C+claims%3A%28%22synthetic+biology%22%29%29&f=false&v=table") %>% print()
```

###


There is something wrong with the claims search as it is report


###Search Strategy

#1. get the total results and reduce on family
#2. rank on citing and retrieve the first 500
#3. rank on family size and retrieve the first 500
#4. retrieve the most recent documents where there will be no large family or citations yet, 

That strategy would cover the most important and the most recent documents on a subject. 

##TO DO Add publication date ranges

Publication date: "https://www.lens.org/lens/search?q=%22synthetic+biology%22&dates=%2Bpub_date%3A19991231-20160101&l=en"
Filing date: "https://www.lens.org/lens/search?q=%22synthetic+biology%22&dates=%2Bfiling_date%3A19991231-20160101&l=en"

YYYYMMDD-

##Document Types: 

Patent Applications and Grants Only (see [types](https://www.lens.org/lens/structured-search))

"https://www.lens.org/lens/search?q=%22synthetic+biology%22&dates=%2Bfiling_date%3A19991231-20160101&types=Patent+Application&types=Granted+Patent&l=en"
